\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage[latin1] { inputenc}
\usepackage{xcolor}
%\topmargin -1cm
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}

\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,backref=page]{hyperref}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand{\comment}[1]{}

\begin{document}

\name{ \sc \Large Meghana Bhat \footnote{\href{https://meghanabht.github.io/meghanabhat.github.io/}{https://meghanabht.github.io/meghanabhat.github.io/}}  \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2in}}
530                           &  Personal email - \\
A-2 Science            & \verb+mbhat.math@gmail.com+  \\ 
Indian Institute of Technology, Dharwad    &  Institutional email- \\
580007 India.                    & \verb+212071001@gmail.com+ \\ 
    
\end{tabular}

%\section{ \sc Webpage} \href{https://www.sites.google.com/view/akshay-hegde}{https://www.sites.google.com/view/akshay-hegde}

\section{\sc Research Interests}
Hilbert functions, Waring rank problem of forms.

\section{\sc Education}

{\bf Indian Institute of Technology Dharwad}
\vspace*{-.1in}

\hspace{0.2cm} Ph.D. in Mathematics  \hfill \textbf{ July 2021- June 2026} 
\vspace{-.35cm}

\hspace{0.4cm} CGPA: 9.56/10


\begin{itemize}

\item Project: Hilbert functions and applications
\item Advisor: Prof. Shreedevi Masuti
\end{itemize}


{\bf Pondicherry University, Pondicherry}\\
\vspace*{-.1in}
\begin{list1}
\item[] M.Sc. Mathematics  \hfill \textbf{July 2019 - July 2021}
% \vspace{-.1cm}

 \hspace{0.2cm} CGPA: 9.49/10
\comment{
\begin{list2}
\vspace*{.05in}
%\item Project Topic: Sharp phase transition in percolation models via randomised algorithms
% \item Advisor: Prof. D. Yogeshwaran
% \item Aggregate 93.3 \% 
\end{list2} 
}

\end{list1}

{\bf Mahatma Gandhi Memorial College, Udupi}
\vspace*{-.1in}

\hspace{0.2cm} Bachelor of Science (Mathematics, Physics, Statistics) \hfill \textbf{ June 2016- June 2019}
\vspace{-.35cm}

\hspace{0.4cm} Percentage: 92.46\%
\section{\sc Honours / \\ Awards} 

Prime Minister's Research Fellowship (2022-26)

INSPIRE Scholarship (SHE) (2016-21)

National Means-Cum-Merit Scholarship Scheme Examination (NMMS) (2012-16)
% {Kovalevskaya Grant for International Congress of Mathematicians- ICM2022}

%{2nd rank in B.Math(Hons.)}

%{\emph{Teachers' Prize}}, 3 times in B.Math(Hons.), awarded for top-3 students each semester

% {SRFP fellow-2020}, by Indian Academy of Sciences

\section{\sc Preprints / \\ Publications}
 %M. Bhat, S. Dubey, S. K. Masuti, T. Okuma, J. K. Verma, K. Watanabe and K. Yoshida. On Gorensteinness of associated graded rings, (\emph Communicated, available at \href{https://arxiv.org/abs/2404.14189}{https://arxiv.org/abs/2404.14189})  
 
 M. Bhat, S. Dubey, S. K. Masuti, T. Okuma, J. K. Verma, K. Watanabe, and K. Yoshida. {\it On Gorensteiness of associated graded rings of filtrations}. arXiv:2404.14189 (2024).

 M. Bhat, S. Dubey, S. K. Masuti. {\it Iarrobino's $Q$-decomposition for ideals}. In preparation. (2024).

 M. Bhat, E. Carlini, S. Dubey, S. K. Masuti. {\it Apolar sets of reducible forms}. In preparation. (2024).


\section{\sc Talks / \\ Posters}
\textit{International conference on local rings and singularities}, IIT Bombay, India, June 2024

\textit{Seminars of Algebra, Algebraic Geometry and their applications}, Politecnico Di Torino, Italy, April 2024

\textit{One day symposium on Algebra and Geometry}, IIT Dharwad, April 2024

% \textit{4th Italian meeting on Probability and Mathematical Statistics}, Rome, Italy, June 2024

% Trinity Talks: Beyond classroom (high-school outreach), March 2024

% Trinity College MCR research showcase talk, November 2023

% Stochastic Analysis group, internal seminar, Oxford, June 2023

% Bangalore probability seminar, April 2023

\section{\sc Research \\ Visits}
Politicnico Di Torino, Italy (Host: Prof. E. Carlini, funded by SERB-SPARC grant of Prof. Shreedevi Masuti), April-May 2024

IIT Bombay, India (Host: Prof. Jugal Verma), June 2023

\section{\sc Conferences /  \\ Workshops } 

{\emph{Introductory workshop : Commutative algebra}}, SL Math Institute Berkeley (MSRI), USA, January 2024

{\emph{School and workshop on Commutative Algebra and Algebraic Geometry in Prime Characteristics and Workshop on Commutative Algebra and Algebraic Geometry in Prime Characteristics}, ICTP Italy, May 2023}

{\emph{Conference on Commutative Algebra and Algebraic Geometry (CoCAAG-2023)}, IIT Hyderabad, India  February 2023}

{\emph{Sagedays 114}, The Institute of Mathematical Sciences, Chennai, July 2022}

% {\emph{Introductory workshop : Commutative algebra}}, SL Math Institute Berkeley (MSRI), USA, January 2024


\section{ \sc Teaching Experience}
TA for Calculus (B.Tech.), Autumn 2024 

TA for Linear Algebra,  Differential Equations-I (B.Tech.), Spring 2024

TA for Complex Analysis, Differential Equations-II (B.Tech.), Autumn 2023

TA for  Calculus-I,II, Linear Algebra (B.Tech.), Spring 2023

TA for Linear Algebra,  Differential Equations-I (B.Tech.), Spring 2022

TA for Complex Analysis, Differential Equations-II (B.Tech.), Autumn 2021

Instructor for the course Operations research (M.Sc.), KCD College Dharwad, Jan-March 2024

Mentor for the Online Foundation Course in Mathematics held online by MTTS  (OFCM-2020) and (OFCM-2023).

\section{\sc Computing \\ Skills} Basics of programming [Language: C] \\
Computer algebra systems (Macaulay2, Singular, CoCoA)\\
Math typesetting in \LaTeX

\section{\sc Extra \\ curricular} Senate representative (PG) (2023-25)\\
DPGC student member (2023-25)\\
PGAPEC student member (2023-25)



%% Coursework commented

\comment{

\section{\sc Graduate Coursework}

\begin{tabular}{@{}p{2.3in}p{3in}}
\begin{list1}
\item Statistical Mechanics with continuous symmetry
\item Random Graphs and Limits
\item Measure Theory and Probability
\item Functional Analysis
\item Large Deviations Theory
\end{list1}
&
\begin{list1}
\item Random Matrix Theory
\item Advanced Probability
\item Topics in Random Walks
\item Fourier Analysis
\item Differential Topology

\end{list1}

\end{tabular}

}

\end{resume}
\end{document}
